GMSE: an R package for generalised management strategy evaluation

### 2017-11-06 notebook/ms/SI1.Rmd
Framework for the new supporting information

---
title: 'GMSE: an R package for generalised management strategy evaluation'
subtitle: 'Supporting Information 2'
author: A. Bradley Duthie, Jeremy J. Cusack, Isabel L. Jones, Erlend B. Nilsen, Roc&#0237;o Pozo, O.
  Sarobidy Rakotonarivo, Bram Van Moorter, and Nils Bunnefeld
date: '`r Sys.Date()`'
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
  html_document: default
  word_document:
    fig_caption: yes
    reference_docx: docx_template.docx
header-includes:
- \usepackage{lineno}
- \linenumbers
linestretch: 1
---

@@

>>>>

---
title: 'GMSE: an R package for generalised management strategy evaluation'
subtitle: 'Supporting Information 1'
author: A. Bradley Duthie, Jeremy J. Cusack, Isabel L. Jones, Erlend B. Nilsen, Roc&#0237;o Pozo, O.
  Sarobidy Rakotonarivo, Bram Van Moorter, and Nils Bunnefeld
date: '`r Sys.Date()`'
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
  html_document: default
  word_document:
    fig_caption: yes
    reference_docx: docx_template.docx
header-includes:
- \usepackage{lineno}
- \linenumbers
linestretch: 1
---

@@

A genetic algorithm is called in the predefined GMSE manager and user models to simulate human decision making. As of GMSE version 0.3.1.9, this includes one independent call to the genetic algorithm for each decision-making agent in every GMSE time step. Therefore, one run of the genetic algorithm occurs to simulate the manager's policy setting decisions in each time step (unless otherwise defined through non-default `manage_freq` values greater than 1), and one run occurs to simulate each individual user's action decisions in each time step (unless otherwise defined through non-default `group_think = TRUE`, in which case one user makes decions that all other users follow identically. Each run of the genetic algorithm mimics the evolution by natural selection of a populaiton of potential manager or user strategies over multiple generations, with the highest fitness strategy in the terminal generation being selected as the one that the manager or user decides to implement. For clarity, as in the main text, we use 'time step' to refer to a full GMSE cycle (in which multiple genetic algorithms may be run) and 'generation' to refer to a single, non-overlapping, generation of potential strategies that evolve within a genetic algorithm (see Figure 1 of the main text). Below, we explain the genetic algorithm in extended detail as it occurs in GMSE v0.3.1.9 (future versions of GMSE might expand upon this framework). We first explain the key data structure used, then provide an overview of the processes of crossover, mutation, cost constraint, fitness evaluation, tournament selection, and replacement. We then explain the fitness functions of managers and users in more detail.

Key data structures used
================================================================================

General overview of key aspects of the genetic algorithm 
================================================================================

Crossover
--------------------------------------------------------------------------------

Mutation
--------------------------------------------------------------------------------

Cost constraint
--------------------------------------------------------------------------------

Fitness evaluation
--------------------------------------------------------------------------------

Tournament selection
--------------------------------------------------------------------------------

Replacement
--------------------------------------------------------------------------------

Detailed explanation of manager and user fitness functions
================================================================================

Manager fitness function
--------------------------------------------------------------------------------

User fitness function
--------------------------------------------------------------------------------
